A novel distributed nature-inspired algorithm for solving optimization problems

### 2021-09-30 paper.tex
Final Updates
Tables and figures label replacement

We present the description of the following sections in our paper. First, we
introduce our algorithm inspired by the Life-Cycle of animal species in
section~\ref{proposal_section}, followed by our experimental configuration and
results in section~\ref{experiments_section}, we analyze and describe some of
our research findings in section~\ref{discussion_section}, and we finalize by
presenting some inferences based on our experiments' results in
section~\ref{conclusions_section}.

\section{Proposal}
\label{proposal_section}
% Always give a unique label
% and use \ref{<label>} for cross-references
% and \cite{<label>} for bibliographic references
% use \sectionmark{}
% to alter or adjust the section heading in the running head

@@

\section{Experiments}
\label{experiments_section}

@@

In our four experiments, we needed to match or balance the experimentation
parameters according to the specifications of the algorithm used by the DEAP
library. This is to be able to verify if our algorithm would also converge on
the solutions in a similar number of evaluations and execution time.
Table~\ref{tab1} shows the OneMax initial configuration for DEAP and Life-Cycle
experiment.

\begin{table}[]
    \centering        
    \caption{OneMax initial configuration for DEAP and Life-Cycle experiment.}\label{tab1}
    \begin{tabular}{|l|l|l|}
    \hline
    \textbf{Configuration} & \textbf{DEAP} & \textbf{Life-Cycle} \\ \hline
    Population & 60 & 60 \\ \hline
    Max Generation & 20 & 20 \\ \hline
    Stagnation & Off & 10 \\ \hline
    Chromosome Length & 20 & 20 \\ \hline
    Target Fitness & 20 & 20 \\ \hline
    Crossover Rate & 100 & 100 \\ \hline
    Mutation Rate & 7 & 7 \\ \hline
    Tournament Rate & 100 & 50 \\ \hline
    Tournament Sample & 3 & 4 \\ \hline
    Open Reproduction Rate & NA & 5 \\ \hline
    Closed Reproduction Rate & NA & 45 \\ \hline
    Max Age & NA & 80 \\ \hline
    Base Approval & NA & 80 \\ \hline
    Goal Approval & NA & 100 \\ \hline
    \end{tabular}
    \end{table}

@@

\subsubsection{Experiment 1}
The goal of our first OneMax experiment was to make sure our
Life-Cycle algorithm worked as expected, converging on the solution. For this
experiment, we intentionally used delays (on the tenth of a second magnitude)
to follow the Life-Cycle algorithm behavior on the console output. For this
experiment, we compared the DEAP algorithm versus the Life-Cycle using ten
processes (on containers) where we show the summarized results in Table~\ref{tab2}, and
Figure~\ref{fig6} shows their Box and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 1 results: OneMax DEAP versus Life-Cycle (10 processes).}\label{tab2}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{OneMax DEAP} & \multicolumn{4}{l|}{Life-Cycle (10P)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 6.5 & 391 & 0.036 & 10,836 & 9.6 & 578 & 6.830 & 85 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle.} \label{fig6}
    \end{figure}

\subsubsection{Experiment 2}
The goal of our second experiment was to confirm the Life-Cycle
algorithm continued working as expected, converging on the solution. For this
experiment, we reduced the time used on delays (now on the thousands of a
second magnitude) to follow the Life-Cycle algorithm behavior. For this
experiment, we only used tournament selection for the reproduction, on the
first configuration running the Life-Cycle on ten processes, versus the second
configuration where we reduced the processes to the minimum basic 5. We show
the summarized results in Table~\ref{tab3}, and Figure~\ref{fig7} shows their Box and Whisker
chart.

\begin{table}[]
    \centering        
    \caption{Experiment 2 results, Life-Cycle Tournament selection: 10 versus 5 processes.}\label{tab3}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{LifeCycle (Tourn. 10P)} & \multicolumn{4}{l|}{LifeCycle (Tourn. 5P)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 7.2 & 434 & 0.740 & 587 & 8.2 & 495 & 0.826 & 599 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig7_experiment02_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 2: Life-Cycle Tournament selection (10 versus 5 processes).} \label{fig7}
    \end{figure}

\subsubsection{Experiment 3}
The goal of our third experiment was to follow and study the
behavior of the Life-Cycle algorithm that continued converging on the solution.
For this experiment, we remained using minimal delays (thousands of a second
magnitude). For this experiment, we only used tournament selection for the
reproduction, on the first configuration running the Life-Cycle on six
processes, two of whom was the Death process, versus the second configuration
where we reduced the processes to the minimum (five) but increasing the (Death)
goal approval range to 115. We show the summarized results in Table~\ref{tab4},
and Figure~\ref{fig8} shows their Box and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 3 results, Life-Cycle Tournament: 6 processes (Death x2) versus 5 processes (80 to 115 goal).}\label{tab4}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{LifeCycle (Tourn. 6P, Death x2)} & \multicolumn{4}{l|}{LifeCycle (Tourn. 5P, 80-115g)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 8.0 & 483 & 0.846 & 571 & 6.4 & 384 & 0.695 & 553 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig8_experiment03_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 processes double Death, versus 5 processes with an 80 to 115 goal approval).} \label{fig8}
    \end{figure}

\subsubsection{Experiment 4}
The goal of our fourth and last experiment was to follow and
study the behavior of the Life-Cycle algorithm that continued converging on the
solution. For this experiment, we remained using minimal delays (thousands of a
second magnitude). For this experiment, we compared the OneMax DEAP
implementation versus the Life-Cycle algorithm, only using tournament selection
for the reproduction, with the Life-Cycle configuration running on the minimum
(five) processes but increasing the (Death) goal approval range to 125. We show
the summarized results in Table~\ref{tab5}, and Figure~\ref{fig9} shows their Box and Whisker
chart.

\begin{table}[]
    \centering        
    \caption{Experiment 4 results, OneMax DEAP versus Life-Cycle Tournament: 5 processes (80 to 125 goal).}\label{tab5}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{OneMax DEAP} & \multicolumn{4}{l|}{Life-Cycle (Tourn. 5P, 80-125g)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 6.5 & 391 & 0.036 & 10,836 & 6.3 & 377 & 0.678 & 556 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig9_experiment4_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 processes with an 80 to 125 goal approval).} \label{fig9}
    \end{figure}

\section{Discussion}
\label{discussion_section}

@@

\section{Conclusions}
\label{conclusions_section}

>>>>

We present the description of the following sections in our paper. First, we
introduce our algorithm inspired by the Life-Cycle of animal species in
section~\ref{section.proposal}, followed by our experimental configuration and
results in section~\ref{section.experiments}, we analyze and describe some of
our research findings in section~\ref{section.discussion}, and we finalize by
presenting some inferences based on our experiments' results in
section~\ref{section.conclusions}.

\section{Proposal}
\label{section.proposal}
% Always give a unique label
% and use \ref{<label>} for cross-references
% and \cite{<label>} for bibliographic references
% use \sectionmark{}
% to alter or adjust the section heading in the running head

@@

\section{Experiments}
\label{section.experiments}

@@

In our four experiments, we needed to match or balance the experimentation
parameters according to the specifications of the algorithm used by the DEAP
library. This is to be able to verify if our algorithm would also converge on
the solutions in a similar number of evaluations and execution time.
Table~\ref{tab.configuration} shows the OneMax initial configuration for DEAP and Life-Cycle
experiment.

\begin{table}[]
    \centering        
    \caption{OneMax initial configuration for DEAP and Life-Cycle experiment.}\label{tab.configuration}
    \begin{tabular}{|l|l|l|}
    \hline
    \textbf{Configuration} & \textbf{DEAP} & \textbf{Life-Cycle} \\ \hline
    Population & 60 & 60 \\ \hline
    Max Generation & 20 & 20 \\ \hline
    Stagnation & Off & 10 \\ \hline
    Chromosome Length & 20 & 20 \\ \hline
    Target Fitness & 20 & 20 \\ \hline
    Crossover Rate & 100 & 100 \\ \hline
    Mutation Rate & 7 & 7 \\ \hline
    Tournament Rate & 100 & 50 \\ \hline
    Tournament Sample & 3 & 4 \\ \hline
    Open Reproduction Rate & NA & 5 \\ \hline
    Closed Reproduction Rate & NA & 45 \\ \hline
    Max Age & NA & 80 \\ \hline
    Base Approval & NA & 80 \\ \hline
    Goal Approval & NA & 100 \\ \hline
    \end{tabular}
    \end{table}

@@

\subsubsection{Experiment 1} The goal of our first OneMax experiment was to
make sure our Life-Cycle algorithm worked as expected, converging on the
solution. For this experiment, we intentionally used delays (on the tenth of a
second magnitude) to follow the Life-Cycle algorithm behavior on the console
output. For this experiment, we compared the DEAP algorithm versus the
Life-Cycle using ten processes (on containers) where we show the summarized
results in Table~\ref{tab.experiment1}, and Figure~\ref{fig.experiment1} shows
their Box and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 1 results: OneMax DEAP versus Life-Cycle (10 processes).}\label{tab.experiment1}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{OneMax DEAP} & \multicolumn{4}{l|}{Life-Cycle (10P)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 6.5 & 391 & 0.036 & 10,836 & 9.6 & 578 & 6.830 & 85 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle.} \label{fig.experiment1}
    \end{figure}

\subsubsection{Experiment 2} The goal of our second experiment was to confirm
the Life-Cycle algorithm continued working as expected, converging on the
solution. For this experiment, we reduced the time used on delays (now on the
thousands of a second magnitude) to follow the Life-Cycle algorithm behavior.
For this experiment, we only used tournament selection for the reproduction, on
the first configuration running the Life-Cycle on ten processes, versus the
second configuration where we reduced the processes to the minimum basic 5. We
show the summarized results in Table~\ref{tab.experiment2}, and
Figure~\ref{fig.experiment2} shows their Box and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 2 results, Life-Cycle Tournament selection: 10 versus 5 processes.}\label{tab.experiment2}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{LifeCycle (Tourn. 10P)} & \multicolumn{4}{l|}{LifeCycle (Tourn. 5P)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 7.2 & 434 & 0.740 & 587 & 8.2 & 495 & 0.826 & 599 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig7_experiment02_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 2: Life-Cycle Tournament selection (10 versus 5 processes).} \label{fig.experiment2}
    \end{figure}

\subsubsection{Experiment 3} The goal of our third experiment was to follow and
study the behavior of the Life-Cycle algorithm that continued converging on the
solution. For this experiment, we remained using minimal delays (thousands of a
second magnitude). For this experiment, we only used tournament selection for
the reproduction, on the first configuration running the Life-Cycle on six
processes, two of whom was the Death process, versus the second configuration
where we reduced the processes to the minimum (five) but increasing the (Death)
goal approval range to 115. We show the summarized results in
Table~\ref{tab.experiment3}, and Figure~\ref{fig.experiment3} shows their Box
and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 3 results, Life-Cycle Tournament: 6 processes (Death x2) versus 5 processes (80 to 115 goal).}\label{tab.experiment3}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{LifeCycle (Tourn. 6P, Death x2)} & \multicolumn{4}{l|}{LifeCycle (Tourn. 5P, 80-115g)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 8.0 & 483 & 0.846 & 571 & 6.4 & 384 & 0.695 & 553 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig8_experiment03_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 processes double Death, versus 5 processes with an 80 to 115 goal approval).} \label{fig.experiment3}
    \end{figure}

\subsubsection{Experiment 4} The goal of our fourth and last experiment was to
follow and study the behavior of the Life-Cycle algorithm that continued
converging on the solution. For this experiment, we remained using minimal
delays (thousands of a second magnitude). For this experiment, we compared the
OneMax DEAP implementation versus the Life-Cycle algorithm, only using
tournament selection for the reproduction, with the Life-Cycle configuration
running on the minimum (five) processes but increasing the (Death) goal
approval range to 125. We show the summarized results in
Table~\ref{tab.experiment4}, and Figure~\ref{fig.experiment4} shows their Box
and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 4 results, OneMax DEAP versus Life-Cycle Tournament: 5 processes (80 to 125 goal).}\label{tab.experiment4}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{OneMax DEAP} & \multicolumn{4}{l|}{Life-Cycle (Tourn. 5P, 80-125g)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 6.5 & 391 & 0.036 & 10,836 & 6.3 & 377 & 0.678 & 556 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig9_experiment4_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 processes with an 80 to 125 goal approval).} \label{fig.experiment4}
    \end{figure}

\section{Discussion}
\label{section.discussion}

@@

\section{Conclusions}
\label{section.conclusions}
